Ionization of molecules by multicharged bared ions by using the stoichiometric model

### 2019-09-19 NewMonti25.tex
symbols changed in origin figures

\documentclass[preprint,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{gensymb}
\usepackage{float}

\usepackage{authblk}

@@

We report the total ionization cross sections by the impact of 
multicharged ions for adenine, cytosine, guanine and thymine in 
Fig.~\ref{fig:crossDNA_1}. For adenine, the agreement with the 
experimental data available (circles)~\cite{iriki2011} is very good 
in our range of validity. To the best of our knowledge, there are not 
experimental data on ion--collision ionization for the rest of the 
molecules. We included electron impact measurements (right--oriented 
triangles)~\cite{rahman2016} with the corresponding equivelocity 
conversion for incident energies higher than 500~keV. In this region, 
the proton and electron cross section should agree. Although the electron 
impact measurements are above our findings for all the molecular targets, 
it is worth stating that our results agree very well with other 
theoretical predictions~\cite{mozejko2003,tan2018}. The symbols used to 
make reference to the proton and electron experimental data will be kept 
for subsequent figures.

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig2.eps}
\caption{Present ionization cross section by impact of six projectiles, 
and experimental values for proton and electron ionization.}
\label{fig:crossDNA_1}
\end{figure}

Our calculations for uracil, DNA backbone, pyrimidine and THF are given in 
Fig.~\ref{fig:crossDNA_2}. 
For uracil, we have good agreement with the experimental 
proton impact measurements (triangle--up) by Itoh~{\it et al.}~\cite{itoh2013}. 
However, for the same target, our theory fails by a factor of two for 
the experimental ionization values by the impact of 
C$^{+4}$~(squares), O$^{+6}$~(circles) and O$^{+8}$~(triangles--down) 
ions~\cite{agnihotri2012,agnihotri2013}.
Nonetheless, it should be stated that our theoretical results coincide 
with calculations by Champion, Rivarola and 
collaborators~\cite{champion2012,agnihotri2012}, which may indicate a 
possible misstep of the experiments. 
For pyrimidine, we show comparison of our results with experimental data
for proton (circles with dash)~\cite{wolff2014} and electron
(stars)~\cite{bug2017} ionization. The electron impact measurements 
agree with our calculations for energies higher than 500keV. 
Unexpectedly, the proton impact cross sections are significantly lower 
than our findings. 
The THF molecule results are compared with proton (squares)~\cite{wang2016} 
and electron~\cite{bug2017,wolf2019,fuss2009} impact measurements, showing
overall good agreement with our theory.

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig3.eps}
\caption{Present ionization cross section by impact of six projectiles, 
and experimental values for proton and electron ionization.}
\label{fig:crossDNA_2}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig4.eps}
\caption{Scaled ionization cross section per weakly bound electron using
(a)~the Toburen numbers $\nu_{\alpha}^T$, and (b) our proposed numbers
$\nu_{\alpha}^{\text{CDW}}$.}
\label{fig:newscaling}
\end{figure}

@@

The new scaled cross sections $\sigma_{e}$ are plotted in Figure~4b. 
A much better sharp band is observed, especially for impact energies 
$E=(0.5-8)$~MeV/amu for $Z=1$ and $Z=2$, and $E=(2.5-8)$~MeV/amu for 
$Z>2$. In fact, the experimental data for ionization of adenine, 
cytosine, thymine, guanine, uracil, pyrimidine and THF by proton impact 
seems to corroborate the new scaling. We also included the electron impact
ionization measurements from Figs.~\ref{fig:crossDNA_1} and 
\ref{fig:crossDNA_2}. It will be interesting to cross--check for 
experiments with higher projectile charge states.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/fig_recta.eps}
\caption{.}
\label{fig:recta}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig5.eps}
\caption{.}
\label{fig:emittedener}
\end{figure}

@@

In Figure~\ref{fig:emittedener} , we estimate $\overline{E}_{\alpha}$ in the 0.5--2 a.u.
velocity range, or equivalently from 15 to 50 eV, for all the targets.
Our results agree with the experimental findings~\cite{surdutovic2018}. 
The dependence of the mean energy value with the projectile charge $Z$ 
is surprisingly sensible, which can duplicate the proton results. 
This effect can be attributed to the depletion caused by the 
multicharged ions to the yields of low energy electrons. In the high 
electron energy regime, the CDW falls on the simple first Born 
approximation, surviving the $Z^{2}$ law. Then, the ratio in 
Eq.~(\ref{40}) cancels out and $\overline{E}_{\alpha}$ becomes a 
universal value independent on $Z$.

Extending the simple stoichiometric model for the mean electron energy
calculation, it results
\begin{equation}
\overline{E}_{M}=\frac{\sum\limits_{\alpha}n_{\alpha}
\overline{E_{\alpha}}}{\sum\limits_{\alpha}n_{\alpha}\sigma_{\alpha}}.
\label{70}
\end{equation}
For impact of H$^{+}$ and He$^{+2}$ on water at 1 MeV/amu, we obtain 
$\overline{E}_{\text{H}_{2}\text{O}}=43.7$ and 45 eV, while the 
experimental values 
on liquid water by Pimblott and LaVerne [xxx] were found to be 51.5 and 
52.2 eV, respectively. Just to stress the importance of the projectile 
charge, for O$^{+8}$ on water, at the same impact energy 1 MeV/amu, 
we obtained $\overline{E}_{\text{H}_{2}\text{O}}=54.7$ eV, which is 25\% 
larger than proton impact result. It is worth noting that there should 
not be any difference if the calculations were carried in first Born 
approximation. We will came back on this issue later.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig6.eps}
\caption{.}
\label{fig:emittedang}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{figuras/levelsDNA.eps}
\caption{Molecular binding energies for four DNA molecules.}
\label{fig:bindener}
\end{figure}

@@

\bibitem{itoh2013} 
A. Itoh, Y. Iriki, M. Imai, C. Champion, and R. D. Rivarola, 
Cross sections for ionization of uracil by MeV-energy-proton impact, 
Phys. Rev. A 88, 052711 (2013).

\bibitem{} in energy and angles~,

\bibitem{champion2012} 
C Champion, M E Galassi, O Foj\'{o}n, H Lekadir, J Hanssen, R D Rivarola,
P F Weck, A N Agnihotri, S Nandi, and L C Tribedi. Ionization of RNA-uracil
by highly charged carbon ions.
J. Phys.: Conf. Ser. 373, 012004 (2012).

\bibitem{agnihotri2012}
A. N. Agnihotri, S. Kasthurirangan, S. Nandi, A.
Kumar, M. E. Galassi, R. D. Rivarola, O. Foj\'{o}n, C. Champion, J. Hanssen,
H. Lekadir, P. F. Weck, and L. C. Tribedi. Ionization of uracil in
collisions with highly charged carbon and oxygen ions of energy 100 keV to
78 MeV. 
Phys. Rev. A 85, 032711 (2012).

\bibitem{agnihotri2013}
A N Agnihotri, S Kasthurirangan, S Nandi, A Kumar, C Champion,, H Lekadir, 
J Hanssen, P FWeck, M E Galassi, R D Rivarola, O Fojon and L C Tribedi, 
Absolute total ionization cross sections of uracil (C4H4N2O2) in 
collisions with MeV energy highly charged carbon, oxygen and fluorine ions
J. Phys. B \textbf{46}, 185201 (2013).

@@

>>>>

\documentclass[preprint,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{gensymb}
\usepackage{float}
\usepackage{authblk}
\usepackage{MnSymbol}

@@

We report the total ionization cross sections by the impact of 
multicharged ions for adenine, cytosine, guanine and thymine in 
Fig.~\ref{fig:crossDNA_1}. For adenine, the agreement with the 
experimental data available~\cite{iriki2011} is very good 
in our range of validity. To the best of our knowledge, there are not 
experimental data on ion--collision ionization for the rest of the 
molecules. We included electron impact measurements~\cite{rahman2016} 
with the corresponding equivelocity 
conversion for incident energies higher than 500~keV. In this region, 
the proton and electron cross section should agree. Although the electron 
impact measurements are above our findings for all the molecular targets, 
it is worth stating that our results agree very well with other 
theoretical predictions~\cite{mozejko2003,tan2018}. 
%The symbols used to make reference to the proton and electron experimental data will be kept for subsequent figures.

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig2.eps}
\caption{Scaled ionization cross section by impact of multicharged ions. 
Experiments: 
$\circ$~\cite{iriki2011} for proton impact and $\square$~\cite{rahman2016} 
for electron impact with equivelocity conversion.}
\label{fig:crossDNA_1}
\end{figure}

Our calculations for uracil, DNA backbone, pyrimidine and THF are given in 
Fig.~\ref{fig:crossDNA_2}. 
For uracil, we have good agreement with the experimental 
proton impact measurements by Itoh~{\it et al.}~\cite{itoh2013}. 
However, for the same target, our theory fails by a factor of two for 
the experimental ionization values by the impact of 
C$^{+4}$, O$^{+6}$ and O$^{+8}$ ions~\cite{agnihotri2012,agnihotri2013}.
Nonetheless, it should be stated that our theoretical results coincide 
with calculations by Champion, Rivarola and 
collaborators~\cite{agnihotri2012,champion2012}, which may indicate a 
possible misstep of the experiments. 
For pyrimidine, we show comparison of our results with experimental data
for proton~\cite{wolff2014} and electron~\cite{bug2017} ionization. 
The electron impact measurements 
agree with our calculations for energies higher than 500keV. 
Unexpectedly, the proton impact cross sections are significantly lower 
than our findings. 
The THF molecule results are compared with proton~\cite{wang2016} 
and electron~\cite{bug2017,wolf2019,fuss2009} impact measurements, showing
overall good agreement with our theory.

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig3.eps}
\caption{Scaled ionization cross section by impact of multicharged ions. 
Experiments: proton impact on $\triangle$ uracil~\cite{itoh2013}, 
$\bigtriangledown$ pyrimidine~\cite{wolff2014} and $\meddiamond$
THF~\cite{wang2016}. Impact of $\ominus$ C$^{+4}$, 
$\boxminus$ C$^{+6}$, O$^{+6}$, F$^{+6}$, and
$\triangle\mkern-14mu-$ O$^{+8}$, F$^{+8}$ on 
uracil~\cite{agnihotri2012,agnihotri2013}. 
Symbols~$\rhd$~\cite{bug2017}, $\lhd$~\cite{wolf2019}, and 
$\medstar$~\cite{fuss2009} for electron impact with equivelocity conversion.}
\label{fig:crossDNA_2}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig4.eps}
\caption{Scaled ionization cross section per weakly bound electron using
(a)~the Toburen numbers $\nu_{\alpha}^T$, and (b) our proposed numbers
$\nu_{\alpha}^{\text{CDW}}$. Experiments: proton impact on 
$\circ$ adenine~\cite{iriki2011}, $\triangle$ uracil~\cite{itoh2013}, 
$\bigtriangledown$ pyrimidine~\cite{wolff2014} and $\meddiamond$ 
THF~\cite{wang2016}; electron impact on $\rhd$ pyrimidine~\cite{bug2017},
and $\lhd$, $\medstar$~\cite{wolf2019,fuss2009} THF.}
\label{fig:newscaling}
\end{figure}

@@

The new scaled cross sections $\sigma_{e}$ are plotted in Figure~4b. 
A much better sharp band is observed, especially for impact energies 
$E=(0.5-8)$~MeV/amu for $Z=1$ and $Z=2$, and $E=(2.5-8)$~MeV/amu for 
$Z>2$. In fact, the experimental data for ionization of 
adenine~\cite{iriki2011}, uracil~\cite{itoh2013}, 
pyrimidine~\cite{wolff2014} and THF~\cite{wang2016} by proton impact 
seems to corroborate the new scaling. 
We also included the electron impact ionization measurements with equivelocity 
conversion on pyrimidine~\cite{bug2017}, and THF~\cite{bug2017,wolf2019,fuss2009}. 
It will be interesting to cross--check for experiments with higher 
projectile charge states.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/fig_recta.eps}
\caption{Ionization cross sections by impact of protons at 0.5, 1 and 2 MeV
in terms of the number of active electrons given by Table~\ref{nn}.
Experiments: $\circ$~adenine~\cite{iriki2011}, $\triangle$ uracil~\cite{itoh2013}, 
$\bigtriangledown$ pyrimidine~\cite{wolff2014}, 
$\blacktriangle$ C2H$_7$N, CH$_5$N, methane and amonia~\cite{lynch1976},
$\bigstar$ amonia and H$_2$~\cite{rudd1985}, and $\bullet$ water~\cite{luna2007}.}
\label{fig:recta}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig5.eps}
\caption{Mean emitted energy distribution for ionization by impact of
multicharged ions.}
\label{fig:emittedener}
\end{figure}

@@

In Figure~\ref{fig:emittedener} , we estimate $\overline{E}_{\alpha}$ in the 0.5--2 a.u.
velocity range, or equivalently from 15 to 50 eV, for all the targets.
Our results agree with the experimental findings~\cite{surdutovic2018}. 
The dependence of the mean energy value with the projectile charge $Z$ 
is surprisingly sensible, which can duplicate the proton results. 
This effect can be attributed to the depletion caused by the 
multicharged ions to the yields of low energy electrons. In the high 
approximation, surviving the $Z^{2}$ law. Then, the ratio in 
Eq.~(\ref{40}) cancels out and $\overline{E}_{\alpha}$ becomes a 
universal value independent on $Z$.

Extending the simple stoichiometric model for the mean electron energy
calculation, it results
\begin{equation}
\overline{E}_{M}=\frac{\sum\limits_{\alpha}n_{\alpha}
\overline{E_{\alpha}}}{\sum\limits_{\alpha}n_{\alpha}\sigma_{\alpha}}.
\label{70}
\end{equation}
For impact of H$^{+}$ and He$^{+2}$ on water at 1 MeV/amu, we obtain 
\mbox{$\overline{E}_{\text{H}_{2}\text{O}}=43.7$} and 45 eV, while the 
experimental values 
on liquid water by Pimblott and LaVerne \cite{pimblott2007} were found 
to be 51.5 and 52.2 eV, respectively. Just to stress the importance of 
the projectile charge, for O$^{+8}$ on water, at the same impact energy 
1 MeV/amu, we obtained \mbox{$\overline{E}_{\text{H}_{2}\text{O}}=54.7$} eV, 
which is 25\% larger than proton impact result. It is worth noting that 
there should not be any difference if the calculations were carried in 
first Born approximation. We will came back on this issue later.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.75\textwidth]{figuras/Fig_finales/Fig6.eps}
\caption{Mean emitted angle distribution for ionization by impact of
multicharged ions.}
\label{fig:emittedang}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{figuras/levelsDNA.eps}
\caption{Theoretical molecular binding energies for adenine, cytosine, 
guanine, thymine and uracil compared to those of atomic constituents.}
\label{fig:bindener}
\end{figure}

@@

\bibitem{itoh2013} 
A. Itoh, Y. Iriki, M. Imai, C. Champion, and R. D. Rivarola, 
Cross sections for ionization of uracil by MeV-energy-proton impact, 
Phys. Rev. A \textbf{88}, 052711 (2013).

%\bibitem{} in energy and angles~,

\bibitem{agnihotri2012}
A. N. Agnihotri, S. Kasthurirangan, S. Nandi, A.
Kumar, M. E. Galassi, R. D. Rivarola, O. Foj\'{o}n, C. Champion, J. Hanssen,
H. Lekadir, P. F. Weck, and L. C. Tribedi. 
Ionization of uracil in collisions with highly charged carbon and oxygen 
ions of energy 100 keV to 78 MeV. 
Phys. Rev. A \text{85}, 032711 (2012).

\bibitem{agnihotri2013}
A N Agnihotri, S Kasthurirangan, S Nandi, A Kumar, C Champion,, H Lekadir, 
J Hanssen, P FWeck, M E Galassi, R D Rivarola, O Fojon and L C Tribedi, 
Absolute total ionization cross sections of uracil (C$_4$H$_4$N$_2$O$_2$) in 
collisions with MeV energy highly charged carbon, oxygen and fluorine ions
J. Phys. B \textbf{46}, 185201 (2013).

\bibitem{champion2012} 
C Champion, M E Galassi, O Foj\'{o}n, H Lekadir, J Hanssen, R D Rivarola,
P F Weck, A N Agnihotri, S Nandi, and L C Tribedi. 
Ionization of RNA-uracil by highly charged carbon ions.
J. Phys.: Conf. Ser. \textbf{373}, 012004 (2012).

@@

\bibitem{lynch1976}
D. J. Lynch, L. H. Toburen, and W. E. Wilson,
Electron emission from methane, ammonia, monomethylamine, and
dimethylamine by 0.25 to 2.0 MeV protons
J. Chem. Phys. \textbf{64}, 2616 (1976).

\bibitem{rudd1985}
M.E. Rudd, Y.-K. Kim, D.H. Madison, J.W. Gallagher,
Electron production in proton collisions: total cross sections,
Review of Modern Physics, \textbf{57}, 965--994 (1985).

\bibitem{luna2007}
H. Luna, A. L. F. de Barros, J. A. Wyer, S. W. J. Scully, J. Lecointre, 
P. M. Y. Garcia, G. M. Sigaud, A. C. F. Santos, V. Senthil, M. B. Shah, 
C. J. Latimer, and E. C. Montenegro,
Water-molecule dissociation by proton and hydrogen impact,
Phys. Rev. A \textbf{75} 042711 (2007).
